\vfill A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications

### 2014-05-16 Paper/paper.tex
Background edits

\title{\vfill A Survey of Web Testing Frameworks and Workflow for Testing Javascript Applications} %\vfill gives us the black space at the top of the page
\author{
By Taggart Ashby \vspace{10pt} \\
Computer Science Department, California Polytechnic State University, San Luis Obispo
}

@@

We have brought together a number of testing tools from the web and created what we feel is a fully-featured, easy to use, testing framework and workflow for Javascript web applications.
\end{abstract}

@@

% - Asynchronous shennanigans
The addition of Javascript to web applications led to a golden age of feature-rich applications with exciting user interface (UI) features that had not before been seen. This set of features and UI improvements came with the complication of asynchronous execution. Unlike traditional multi-threaded software, however, the developer is not given access to individual threads but is stuck with just the main thread. This sort of implementation is essential for dealing with asynchronous events like button clicks, loading data separately so as not to hold up the web page, and a variety of other niceties, but is the cause of major headaches in testing. Without access to individual threads, the developer has to either write synchronous code that will be slow and not user-friendly, or rely on other mechanisms that allow code to be sequenced. Often it is hard to get code properly sequenced and it requires changing straightforward functions to a hideous amalgamation of callbacks.

@@

\subsection{Web Application Strengths}
Web applications are great for both developers and consumers. They have a number of characteristics that make them more desirable than shrink-wrap software. These attributes are versioning, availability, platform independence, and the ability to rapidly prototype.

@@

\subsubsection{Availability}
Web application are available anywhere there's internet. No need to install anything on a given device most of the time. Due to the ever-increasing popularity of mobile devices, most applications have both mobile and full versions of their software and so the application is ``with'' the user all the time.

\subsubsection{Multi-platform}
Very similar to the availability strength, web applications are platform independent. Whether the user is on their phone, tablet, laptop, or PC, the application only requires a web browser with certain functionality and in this day and age all devices come equipped with browsers that should have no problems.

\subsubsection{Rapid Prototyping}
Web applications are fantastic for rapid prototyping because of all of the strengths discussed above. An idea can be prototyped and posted on a website quickly and rapid iteration can occur without the user even necessarily noticing. There are a number of web tools that will outline where users are clicking, what features they're using, how long they're spending on a given page or step of a process, and a number of other metrics that can make iterations more directed and effective.

@@

As the web is being increasingly used on mobile devices, HTML5 also introduces geolocation functionality. This funcationality requires user approval, but once that approval is gained, the web application has access to a rough idea of where the user is located. When used on devices that have GPS, such as phones and tablets, this area is more defined and a stronger lock on the user's position can be obtained. This geolocation functionality has opened the door for brand new types of web applications that can much more closely tie in with what the user is seeing or the area that they are in. For example, ads can be more targeted or an application can display distances to nearby points of interest.

@@

%\todo{THIS NEEDS TO MOVE OR CHANGE SUBSECTION TO `WEB APPLICATIONS'}
\paragraph{Node.JS}
As a quick aside, it will be useful to have information about Node.JS as it is used in the sample application and the evaluation applicaiton. Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.'' \cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

@@

Client-side programming is done in a language that the browser understands, most frequently Javascript. Though not technically programming languages, client-side programming is also done through HTML and CSS which control the look and feel of web pages.

@@

\subsection{What is testing?}
IEEE defines software testing as ``the dynamic verification of the behavior of a program on a finite set of test cases, suitably selected from the usually infinite executions domain, against the expected behavior.'' \cite{TestingDefinition} Put a bit more simply, software testing is the process of making sure the program does what it is supposed to.

There are a number of different types of tests and testing concept, we will just focus on Unit Testing, Continuous Integration, and Acceptance Testing.

\subsubsection{Unit Testing}
Unit testing is the testing of specific functions and functionality, or ``test units.'' Test units are ``A set of one or more computer program modules together with associated control data, [...] usage procedures, and operating procedures taht satisfy the following conditions: 1) All modules are from a single computer program. 2) At least one of the new or changed modules in the set has not completed the unit test. 3) The set of modules together with its associated data and procedures are the sole object of a testing process.'' \cite{UnitTestDefinition} Generally this means the testing of individual functions but can extend to a set of functions that produce a single module of functionality. What sets Unit Testing apart from other types of testing is that tests focus on one portion of the code or system rather than interactions between modules or the entire system.

@@

\subsubsection{Continuous Integration}
The original definition of Continuous Integration involves the idea of developers committing from their  branches to a master branch daily so that changes are continuously integrated in an effort to make sure all branches can, in fact, be integrated. It has since evolved into a more general idea of a tool that runs commands after each commit to a repository. This commands generally encompass running unit tests, integration tests, user interface tests, and also often publishing and disseminating notifications to interested parties. This is invaluable feedback because the developer can see if they're making progress in the right direction as they write code, as opposed to a situation in which the developer finishes coding and finds out they've made a bad assumption or decision between this commit and the last.

@@

In an effort to automate this, some developers create ``User Stories'' which are automated tests that run a series of functions described by customers or an SRS. These User Stories are often written in a seperate language that is more like english than code. The traditional User Story template is: ``As a <role>, I want <goal/desire> so that <benefit>.'' For example: ``As a supervisor, I want to find my employees by their employee ID.'' These user stories are then broken down into more specific steps that can be automated.

@@

What we see here is that the earlier a defect is introduced the more it costs to fix it later. Of particular note is that the costs are roughly exponential, not linear. The longer a bug lies undetected, the increasingly harder it becomes to fix that bug. On the flip side, it's relatively easy to fix a bug that was introduced in the same stage that it is found, e.g. introducing a coding bug during ``Construction'' and fixing it while still writing code, prior to the ``System Test'' phase.

@@

\subsubsection{The Average Web Application}
In an effort to create a good workflow and collection of tools, we have chosen to focus on web applications that uses Node.js, Javascript, Cloud Services, and a backing Database when searching for our tools. This choice was made because of the popularity of that kind of set up, as well as the fact that our evaluation application was set up in that way.

@@

Javascript was chosen because it used in over 87\% of all websites. \cite{JSUsage}

@@

%- Node.js
%- Browser based
%- Javascript
%- Database
%- Open-source

@@

%- Code Coverage!
Intern includes configurable code coverage metrics on tests by default. Running unit tests gives the number of lines covered (ran) by the tests. Code coverage is provided by another Javascript library, Istanbul, created by Krishnan Anantheswaran \cite{Istanbul}.

@@

Having the ability to automatically run browser tests at any point takes a huge burden off of the web developer and allows for UI testing in addition to behind the scenes functionality testing. Whenever code is changed that may affect the UI flow or functionality, Selenium tests can be run withou the need for developers to manually click all of the HTML elements and input information in the relevant places.

Selenium's node incarnation is out-of-date and as such we had to change the selenium package to use the latest version of Selenium that works with the latest version of browsers. This required us to edit some of the javascript files that ran Selenium from the console using node. At the time of this writing, the Selenium node package was using Selenium 2.20 from over two years ago. The latest Selenium version is 2.40.

Selenium was written with maximum functionality and language flexability in mind and therefore can be incredibly verbose.

The Selenium WebDriver has APIs for a variety of programming languages including: Javascript, C, Java, and Python.

\subsubsection{Nightwatchjs\cite{NightwatchJS}}
Nightwatch is a Javascript testing library that wraps Selenium in an effort to make browser testing more concise and straightforward. Nightwatch uses Node.js' assertion library paired with Selenium's WebDriver to both run browser automation and also report test results.

@@

Semaphore was originally designed for only Ruby applications but in January of 2014 they announced official support for Node.js and Javascript and as of February 26th they now offer official support for Clojure projects.\cite{SemaphoreBlog} These types of projects require no setup or files in the repository, Semaphore automatically detects project type and auto-fills build steps. Their ``supported stack'' page also lists C/C++, Java, Perl, and Python, but those must be configured manually.

@@

\subsubsection{Sauce Labs\cite{SauceLabs}}
Sauce Labs is an online service that gives you access to a variety of browsers and browser options. They outline the options available to the developer as follows: Selenium, Javascript, Mobile, Manual. Sauce Labs will start up a Selenium server and run the developer's Selenium tests, they can run unit tests using their Javascript service, they allow access to a variety of mobile device browsers and resolution, and they offer the ability to manually look at a web application in different browser configurations.

@@

\subsubsection{Grunt.js\cite{GruntJS}}
Grunt.js is a task-runner for Javascript. What Grunt does is automate routine tasks like linting, testing, copying files, and updating modules. The developer writes Grunt scripts that outline the necessary tasks and then can run them on the commandline with the \lstinline{grunt} command.

@@

\subsubsection{Setting up Grunt}
Getting Grunt set up just the way the developer wants it is likely the most involved, but there are a myriad of examples and sample scripts to help them through. Installation is the same as we've seen before, \lstinline{npm install -g grunt-cli}. After installation the developer will need to create a ``Gruntfile'' which is just a Javascript file called ``Gruntfile.js''. Inside the Gruntfile are all of the command names and procedures that the developer wants. As the documentation outlines: ``A Gruntfile is comprised of the following parts: 1) The \"wrapper\" function 2) Project and task configuration 3) Loading Grunt plugins and tasks 4) Custom tasks''.

@@

\subsubsection{``JAWS: A Javascript API for the Efficient Testing and Integration of Semantic Web Services'' \cite{JAWS}}
A researcher from Ford Motor Company published a paper regarding an API, called JAWS (Javascript, AJAX, Web Service), to facilitate testing and integration of Semantic Web Services. Semantic Web Services (SWS) are the server side of machine-to-machine interaction via the internet. This is opposed to machine-to-human interaction such as web pages that one visits personally. SWS use markup that is detailed and sophisticated which conforms to certain standards but is not human-readable.

>>>>

\title{\vfill A Survey of Web Testing Frameworks and Workflow for Testing JavaScript Applications} %\vfill gives us the black space at the top of the page
\author{
By Taggart Ashby \vspace{10pt} \\
Computer Science Department, California Polytechnic State University, San Luis Obispo
}

@@

We have brought together a number of testing tools from the web and created what we feel is a fully-featured, easy to use, testing framework and workflow for JavaScript web applications.
\end{abstract}

@@

% - Asynchronous shennanigans
The addition of JavaScript to web applications led to a golden age of feature-rich applications with exciting user interface (UI) features that had not before been seen. This set of features and UI improvements came with the complication of asynchronous execution. Unlike traditional multi-threaded software, however, the developer is not given access to individual threads but is stuck with just the main thread. This sort of implementation is essential for dealing with asynchronous events like button clicks, loading data separately so as not to hold up the web page, and a variety of other niceties, but is the cause of major headaches in testing. Without access to individual threads, the developer has to either write synchronous code that will be slow and not user-friendly, or rely on other mechanisms that allow code to be sequenced. Often it is hard to get code properly sequenced and it requires changing straightforward functions to a hideous amalgamation of callbacks.

@@

\subsection{Web Application Strengths}
Web applications are great for both developers and consumers. They have a number of characteristics that make them more desirable than shrink-wrap software. These attributes include versioning, availability, platform independence, and the ability to rapidly prototype.

@@

\subsubsection{Availability}
Web application are available anywhere there's internet. There is no need to install anything on a given device. Due to the ever-increasing popularity of mobile devices, most applications have both mobile and full versions of their software and so the application is ``with'' the user all the time. This instant and continuous availability means that users only have to know how to use a web browser in order to access the application.

\subsubsection{Multi-platform}
Very similar to the availability strength, web applications are platform independent. Whether the user is on their phone, tablet, laptop, or PC, the application only requires a web browser with certain functionality and in this day and age all devices come equipped with browsers that should have no problems. This also means that the developer need not, generally, worry about hardware configurations, conflicting software, and other problems that can arise in desktop applications.

\subsubsection{Rapid Prototyping}
Web applications are fantastic for rapid prototyping because of all of the strengths discussed above. An idea can be prototyped and posted on a website quickly and rapid iteration can occur without the user even necessarily noticing. There are a number of web tools that will record where users are clicking, what features they're using, how long they're spending on a given page or step of a process, and a number of other metrics that can make iterations more directed and effective.

@@

As the web is being increasingly used on mobile devices, HTML5 also introduces geolocation functionality. This functionality requires user approval, but once that approval is gained, the web application has access to a rough idea of where the user is located. When used on devices that have GPS, such as phones and tablets, this area is more defined and a stronger lock on the user's position can be obtained. This geolocation functionality has opened the door for brand new types of web applications that can much more closely tie in with what the user is seeing or the area that they are in. For example, advertisements can be more targeted or an application can display distances to nearby points of interest.

@@

%\todo{THIS NEEDS TO MOVE OR CHANGE SUBSECTION TO `WEB APPLICATIONS'}
\paragraph{Node.JS}
As a quick aside, it will be useful to have information about Node.JS as it is used in the sample application and the evaluation application. Node.JS, often called simply Node, is a JavaScript API for creating and running servers. ``Node's goal is to provide an easy way to build scalable network programs.'' \cite{Node} Node was created in 2009 and is sponsored by Joyent. Node does not use thread-based networking, instead opting for a single-threaded event loop and non-blocking I/O. Node allows developers to create and control web servers without the need for external software, such as Apache, commonly found in other sites.

@@

Client-side programming is done in a language that the browser understands, most frequently JavaScript. Though not technically programming languages, client-side programming is also done through HTML and CSS which control the look and feel of web pages.

@@

\subsection{What is Testing?}
IEEE defines software testing as ``the dynamic verification of the behavior of a program on a finite set of test cases, suitably selected from the usually infinite executions domain, against the expected behavior.'' \cite{TestingDefinition} Put a bit more simply, software testing is the process of making sure the program does what it is supposed to.

There are a number of different types of tests and testing concepts, we will just focus on Unit Testing, Continuous Integration, and Acceptance Testing.

\subsubsection{Unit Testing}
Unit testing is the testing of specific functions and functionality, or ``test units.'' Test units are ``A set of one or more computer program modules together with associated control data, [...] usage procedures, and operating procedures that satisfy the following conditions: 1) All modules are from a single computer program. 2) At least one of the new or changed modules in the set has not completed the unit test. 3) The set of modules together with its associated data and procedures are the sole object of a testing process.'' \cite{UnitTestDefinition} Generally this means the testing of individual functions but can extend to a set of functions that produce a single module of functionality. What sets Unit Testing apart from other types of testing is that tests focus on one portion of the code or system rather than interactions between modules or the entire system.

@@

\subsubsection{Continuous Integration}
The original definition of Continuous Integration involves the idea of developers committing from their  branches to a master branch daily so that changes are continuously integrated in an effort to make sure all branches can, in fact, be integrated. It has since evolved into a more general idea of a tool that runs commands after each commit to a repository. These commands generally encompass running unit tests, integration tests, user interface tests, and also often publishing and disseminating notifications to interested parties. This is invaluable feedback because the developer can see if they're making progress in the right direction as they write code, as opposed to a situation in which the developer finishes coding and finds out they've made a bad assumption or decision between this commit and the last.

@@

In an effort to automate this, some developers create ``User Stories'' which are automated tests that run a series of functions described by customers or an SRS. These User Stories are often written in a separate language that is more like English than code. The traditional User Story template is: ``As a <role>, I want <goal/desire> so that <benefit>.'' For example: ``As a supervisor, I want to find my employees by their employee ID.'' These user stories are then broken down into more specific steps that can be automated.

@@

What we see here is that the earlier a defect is introduced the more it costs to fix it later. Of particular note is that the costs are roughly exponential, not linear. It's relatively easy to fix a bug that was introduced in the same stage that it is found, e.g. introducing a coding bug during ``Construction'' and fixing it while still writing code, prior to the ``System Test'' phase. The longer a bug lies undetected, the increasingly harder it becomes to fix that bug.

@@

\subsubsection{The Average Web Application}
In an effort to create a good workflow and collection of tools, we have chosen to focus on web applications that uses Node.js, JavaScript, Cloud Services, and a backing Database when searching for our tools. This choice was made because of the popularity of that kind of set up, as well as the fact that our evaluation application was set up in that way.

@@

JavaScript was chosen because it used in over 87\% of all websites. \cite{JSUsage}

@@

%- Node.js
%- Browser based
%- JavaScript
%- Database
%- Open-source

@@

%- Code Coverage!
Intern includes configurable code coverage metrics on tests by default. Running unit tests gives the number of lines covered (ran) by the tests. Code coverage is provided by another JavaScript library, Istanbul, created by Krishnan Anantheswaran \cite{Istanbul}.

@@

Having the ability to automatically run browser tests at any point takes a huge burden off of the web developer and allows for UI testing in addition to behind the scenes functionality testing. Whenever code is changed that may affect the UI flow or functionality, Selenium tests can be run without the need for developers to manually click all of the HTML elements and input information in the relevant places.

Selenium's node incarnation is out-of-date and as such we had to change the selenium package to use the latest version of Selenium that works with the latest version of browsers. This required us to edit some of the JavaScript files that ran Selenium from the console using node. At the time of this writing, the Selenium node package was using Selenium 2.20 from over two years ago. The latest Selenium version is 2.40.

Selenium was written with maximum functionality and language flexibility in mind and therefore can be incredibly verbose.

The Selenium WebDriver has APIs for a variety of programming languages including: JavaScript, C, Java, and Python.

\subsubsection{Nightwatchjs\cite{NightwatchJS}}
Nightwatch is a JavaScript testing library that wraps Selenium in an effort to make browser testing more concise and straightforward. Nightwatch uses Node.js' assertion library paired with Selenium's WebDriver to both run browser automation and also report test results.

@@

Semaphore was originally designed for only Ruby applications but in January of 2014 they announced official support for Node.js and JavaScript and as of February 26th they now offer official support for Clojure projects.\cite{SemaphoreBlog} These types of projects require no setup or files in the repository, Semaphore automatically detects project type and auto-fills build steps. Their ``supported stack'' page also lists C/C++, Java, Perl, and Python, but those must be configured manually.

@@

\subsubsection{Sauce Labs\cite{SauceLabs}}
Sauce Labs is an online service that gives you access to a variety of browsers and browser options. They outline the options available to the developer as follows: Selenium, JavaScript, Mobile, Manual. Sauce Labs will start up a Selenium server and run the developer's Selenium tests, they can run unit tests using their JavaScript service, they allow access to a variety of mobile device browsers and resolution, and they offer the ability to manually look at a web application in different browser configurations.

@@

\subsubsection{Grunt.js\cite{GruntJS}}
Grunt.js is a task-runner for JavaScript. What Grunt does is automate routine tasks like linting, testing, copying files, and updating modules. The developer writes Grunt scripts that outline the necessary tasks and then can run them on the commandline with the \lstinline{grunt} command.

@@

\subsubsection{Setting up Grunt}
Getting Grunt set up just the way the developer wants it is likely the most involved, but there are a myriad of examples and sample scripts to help them through. Installation is the same as we've seen before, \lstinline{npm install -g grunt-cli}. After installation the developer will need to create a ``Gruntfile'' which is just a JavaScript file called ``Gruntfile.js''. Inside the Gruntfile are all of the command names and procedures that the developer wants. As the documentation outlines: ``A Gruntfile is comprised of the following parts: 1) The \"wrapper\" function 2) Project and task configuration 3) Loading Grunt plugins and tasks 4) Custom tasks''.

@@

\subsubsection{``JAWS: A JavaScript API for the Efficient Testing and Integration of Semantic Web Services'' \cite{JAWS}}
A researcher from Ford Motor Company published a paper regarding an API, called JAWS (JavaScript, AJAX, Web Service), to facilitate testing and integration of Semantic Web Services. Semantic Web Services (SWS) are the server side of machine-to-machine interaction via the internet. This is opposed to machine-to-human interaction such as web pages that one visits personally. SWS use markup that is detailed and sophisticated which conforms to certain standards but is not human-readable.
